Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-26 finnormal-nodalida-2015/finnormal2015.tex
future work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58598 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

Although a reasonable size for a test corpus, the corpus is still too small for 
wide-coverage experiments. We intend to expand the corpus size to at least 10,000
words. Another weakness of the corpus is that it contains text from a single author,
we would ideally like to add texts from other authors and other colloquial genres. Although
the challenge here is finding text that is both free of privacy issues and available
to release under a free/open-source licence.

As for the methods, we would like to follow \newcite{scannell2014} in incorporating
`translation' probabilities into our normalisation model. Our current model relies 
exclusively on the target-language model probability, however some rules may be more
reliable or probable than others.
